---
title: "Gaming System anaysis"
output: html_document
---

A gaming system contains the following fields 
game_id,player_id,played date and points

# Question 1
```{r}
x<-rep(1:5,times=200)
game_id<-sample(x)
game_id

player_X<-rep(75:124,times = 20)
player_id<-sample(player_X)
player_id

test_date1 <- as.Date(runif(1000, as.integer(as.Date("2021-08-01")), as.integer(as.Date("2021-08-30"))), origin = "1970-01-01")
test_date1

points<-floor(runif(1000, min=75, max=200))
points
```

Now we will combine them into a dataframe

# Question 2
test_date1<-as.Date(test_date1)
data1<-as.data.frame(game_id,player_id,test_date1,points)
head(data1)

Writing mtcars data to a csv file
write_csv(data1, path = "Games.csv")

# Question3 

#Now we will import our synthesized data
```{r}
library(readr)
Games <- read_csv("Games.csv")
head(Games)
```

```{r}
#find out the top five players by points in each games and display the results

head(Games)
dat1<-Games[,c(2,3,5)]
head(dat1)

library(dplyr)

new_dat1 <- dat1 %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(new_dat1)
#the top players are as follows
```

# Question 3b)
```{r}
#find the bottom five players by points in each of the games and display the results
#game_id,player
new_dat2<-arrange(new_dat1,points)



head(new_dat2)

#the bottom 5 players are as follows
```

# Question 3c

```{r}
#find out the player whose total points in the game is greatern than the average of all players
#pointsof that game hint-if average points of all players in a game is 90 then find out all the 
#top 5 players


game_id1<-filter(Games, game_id == "1")
head(game_id1)
game_id1$greater<-ifelse(game_id1$points>=mean(points),"yes","NO")
#the following displays the resulta of game 1
head(game_id1)


game_id2<-filter(Games, game_id == "2")
game_id2$greater<-ifelse(game_id2$points>=mean(points),"yes","NO")
#the following displays results for game 2
head(game_id2)

game_id3<-filter(Games, game_id == "3")
game_id3$greater<-ifelse(game_id2$points>=mean(points),"yes","NO")
#the following displays results for game 3
head(game_id3)

game_id4<-filter(Games, game_id == "4")
game_id4$greater<-ifelse(game_id4$points>=mean(points),"yes","NO")
#the following displays results for game 4
head(game_id4)

game_id5<-filter(Games, game_id == "5")
game_id4$greater<-ifelse(game_id4$points>=mean(points),"yes","NO")
#the following displays results for game 5
head(game_id5)


````
# Question 4c

```{r}
df5<-Games %>% 
  mutate(week = cut.Date(test_date1, breaks = "1 week", labels = FALSE)) %>% 
  arrange(test_date1)

week_1<-filter(df5, week == "1")

week_1_new <- week_1 %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(week_1_new)

week_2<-filter(df5, week == "2")

week_2_new <- week_2 %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(week_2_new)

     
week_3<-filter(df5, week == "3")

week_3_new <- week_3 %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(week_3_new)

week_4<-filter(df5, week == "4")

week_4_new <- week_4 %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(week_4_new)
````

# Question 4d

```{r}
#Bi weeekly

biweek_one<-filter(df5, week == 1|2)
head(biweek_one)

biweek_one <- biweek_one %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(biweek_one)

biweek_two<-filter(df5, week == 3|4)

biweek_two <- biweek_two %>% 
  # desc orders from largest to smallest
  arrange(desc(points)) %>%
  # select subsets the columns you want
  select(game_id,player_id,points)

head(biweek_two)
````

# Git operations

git checkout -b new-branch

```{r}
#this was done create a repository them from the Shell (Tools > Shell)
```

https://github.com/johnwafula/challenges-francois.
```{r}
#forkin was done at this spot on github
```

git remote add upstream https://github.com/r-johnwafula/challenges-francois`

```{r}
#branching operations
```